Kaggle-in-class Data Challenges Can Boost Student Learning

### 2019-02-08 paper-kaggle.Rmd
changes to comparison plot

Kaggle [@kaggle] is well-known for the data competitions, some richly funded. It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set. One of the well-known competitions is the ``Titanic: Machine Learning from Disaster'' in which, mainly the beginners, can practice their skills to predict survival on the Titanic and get familiar with the Kaggle platform and some of the machine learning techniques.

*Di any``famous'' data competition examples ???*

The competitors participating in these competitions have different motivations, but it is mainly fame and financial reward for the winner. 
Occasionally, inventors of new methods and algorithms use Kaggle competitions as a platform to prove the superiority of their methods. A famous example are Geoffrey Hinton and George Dahl with deep neural networks and Tianqi Chen and Carlos Guestrin with XGBoost.

Individuals and organizations that contribute the data and open it for a competition gain expertise from many professionals at once. This increases the chance for an improved and innovative solution to their problem.

In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions. These competitions can be private, limited to members of a university course, and are easy to setup. This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.

@@

Finding data for a competition may take some time. It is not recommended to take freely available data sets from the Internet. A clever student will always try to check if the data is on the web. If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model. As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use. In such a case, the data set and particularly the target values will be unfamiliar to the students.

>>>>

Kaggle [@kaggle] is well-known for the data competitions, some richly funded. It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set. In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions. These competitions can be private, limited to members of a university course, and are easy to setup. This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.

@@
